04_DESeq_sexes_manipulate

### 2019-12-02 analysis/04_DESeq2_sexes_manipulate.Rmd
better volcanos

```{r pitplot, eval = T}
a <- plot.volcano(m.inc.d3.m.inc.d9, "treatment", "m.inc.d9", "m.inc.d3",  colorsvolcano)
b <- plot.volcano(m.inc.d9.m.inc.d17, "treatment", "m.inc.d17", "m.inc.d9",  colorsvolcano)
c <- plot.volcano(m.inc.d17.m.n2, "treatment",  "m.n2", "m.inc.d17", colorsvolcano) 
d <- plot.volcano(m.n2.m.inc.d8, "treatment", "m.inc.d8", "m.n2",  colorsvolcano) 
e <- plot.volcano(m.inc.d8.prolong, "treatment", "prolong", "m.inc.d8",  colorsvolcano) 
f <- plot.volcano(prolong.extend, "treatment", "extend",  "prolong",colorsvolcano)

>>>>

```{r pitplot, eval = T, fig.height=3}
a <- plot.volcano(m.inc.d3.m.inc.d9, "treatment", "m.inc.d9", "m.inc.d3",  colorsvolcano)
b <- plot.volcano(m.inc.d9.m.inc.d17, "treatment", "m.inc.d17", "m.inc.d9",  colorsvolcano)
c <- plot.volcano(m.inc.d17.m.n2, "treatment",  "m.n2", "m.inc.d17", colorsvolcano) 
d <- plot.volcano(m.n2.m.inc.d8, "treatment", "m.inc.d8", "m.n2",  colorsvolcano) 
e <- plot.volcano(m.inc.d8.prolong, "treatment", "prolong", "m.inc.d8",  colorsvolcano) 
f <- plot.volcano(prolong.extend, "treatment", "extend",  "prolong",colorsvolcano)
